Manuscript

### 2017-08-03 manuscript.Rmd
Updated regression equation to Boston variable names.

---
title: "Manuscript"
author: "Nico Boyd, Greg Macfarlane, Kari Watkins, Dave Ederer"
date: "6/16/2017"
output:
  pdf_document: default
  html_document: default
---

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
# regression_data[[2]]["park_ls"] <- calculate_park_logsums(
#   boston_tracts, boston_parks, betas = c(.00001, -30))
# regression_data[[3]]["park_ls"] <- calculate_park_logsums(
#   nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

We looked at income and it doesn't matter.
```{r regression_eq}
base_formula <- formula(
  ~ log(Pop_Density) + FulltimeWork + 
    CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)

@@

```{r linear_models}
# this lets us run all of the linear models (for all the cities) in like ten 
# lines of code
dependent_variables <- c("OBESITY", "PhysAct", "MENTAL")

@@

@@

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(
  base_sem$OBESITY$denver, park_sem$OBESITY$denver,
  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver
)

>>>>

---
title: "Manuscript"
author: "Nico Boyd, Greg Macfarlane, Kari Watkins, Dave Ederer"
date: "6/16/2017"
output:
  html_document: default
  pdf_document: default
---

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
#regression_data[[2]]["park_ls"] <- calculate_park_logsums(
 # boston_tracts, boston_parks, betas = c(.00001, -30))
#regression_data[[3]]["park_ls"] <- calculate_park_logsums(
 # nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

We looked at income and it doesn't matter.
```{r regression_eq}
base_formula <- formula(
  ~ log(Pop_Density) + FulltimeWork + 
    CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)

@@

```{r linear_models}
# this lets us run all of the linear models (for all the cities) in like ten 
# lines of code
dependent_variables <- c("OBESITY", "Phys_Act", "MENTAL")

@@

  names(models) <- cities[1:3]
  return(models)
})

@@

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(
  #base_sem$OBESITY$denver, park_sem$OBESITY$denver,
  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver,
  )
